Trifunctional Sphingosine

### 2025-03-12 LipidProbe/1-10_FattyAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional 1-10 Fatty Acid](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
:::

@@

(CC CNET plot failed in production)

@@

(MF CNET plot failed in production)

@@

(BP CNET plot failed in production)
:::

>>>>

:::{.border}
::: {layout="[[-25,75], [100]]"}
![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)

Chemical structures drawn by Berit Blume.
:::
:::

@@

@@

@@

### 2025-03-12 LipidProbe/8-3_FattyAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional 8-3 Fatty Acid](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
:::

@@

(MF CNET plot failed in production)
:::

>>>>

:::{.border}
::: {layout="[[-25,75], [100]]"}
![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)

Chemical structures drawn by Berit Blume.
:::
:::

@@

### 2025-03-12 LipidProbe/PhosphatidicAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional Phosphatidic Acid](/LipidProbe/Structures/TF_PA.png)
:::

>>>>

:::{.border}
::: {layout="[[-15,85], [100]]"}
![Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)

![Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)

Chemical structures drawn by Berit Blume.
:::
:::

### 2025-03-12 LipidProbe/Phosphatidylethanolamine.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional Phosphatidylethanolamine](/LipidProbe/Structures/TF_PE.png)
:::

>>>>

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
![Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)

![Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)

Chemical structures drawn by Berit Blume.
:::
:::

:::{.border}
![Trifunctional Phosphatidylethanolamine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PE.png)
:::

### 2025-03-12 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
updating structures

:::{.border}
![Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
:::

>>>>

:::{.border}
::: {layout="[[-1.5,98.5], [100]]"}
![Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)

![Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)

Chemical structures drawn by Berit Blume.
:::
:::

### 2025-03-12 LipidProbe/Sphinganine.qmd
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional Sphinganine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphinganine.png)
:::

>>>>

:::{.border}
::: {layout="[[100], [100]]"}
![Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)

![Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)

Chemical structures drawn by Berit Blume.
:::
:::

### 2025-03-12 LipidProbe/Sphingosine.qmd
editing from Frank's suggestions, removing CNET
updating structures

:::{.border}
![Trifunctional Sphingosine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphingosine.png)
:::

>>>>

:::{.border}
::: {layout="[[100], [100]]"}
![Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)

![Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)

Chemical structures drawn by Berit Blume.
:::
:::
